18th International Satisfiability Modulo Theories Competition (SMT-COMP 2023): Rules and Procedures

### 2023-05-21 rules/rules23.tex
Clarified the model validation changes and the different types of participating tools.

  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's
    competition introduced the experimental divisions QF\_FPArith
    (excluding the logics QF\_ABVFP, QF\_AUFBVFP, and QF\_ABVFPLRA).
  %
  This year these divisions will no longer be experimental.
  %
  In addition, we add this year the new experimental division for
  arrays, non-linear arithmetic and for datatypes.  These include the divisions
  QF\_NonLinearIntArith, QF\_NonLinearRealArith,
  QF\_Equality+NonLinearArithm,
  and QF\_Datatypes.
%
  \rationale{Last year's divisions ran successfully, so there
    is no reason to keep them experimental.
    %
    For the new divisions, as before, given the inconsistencies across different
    model producing solvers, we proceed in an experimental fashion to push for
    model standardization. We exclude logics containing arrays since
    there is no standardized way of expressing array model values and
    we do not want to add too many new logics.}

@@

\header{Wrapper Tool.}
%
A \emph{wrapper tool} is defined as any solver that calls one or more other SMT
solvers (the \emph{wrapped solvers}). Its system description \textbf{must}
explicitly acknowledge and state the \textbf{exact} version of any solvers that
it wraps.  It \textbf{must} further make clear technical innovations by which
the wrapper tool expects to improve on the wrapped solvers.

\header{Derived Tool.}
%
A \emph{derived tool} is defined as any solver that is \emph{based on and
extends} another SMT solver (the \emph{base solver}) from a different
group of authors.  Its system description
\textbf{must} explicitly acknowledge
the solver it is based on and extends.  It \textbf{must} further make clear
technical innovations by which the derived tool expects to improve on the
original solver.  A derived tool \textbf{must} follow the \emph{naming convention}
{[name of base solver]-[my solver name]}.

@@

\header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
QF\_DataTypes, QF\_Equality,
QF\_Equality+Bitvec,
QF\_Equality+(Non)LinearArith,  
QF\_(Non)LinearIntArith, and QF\_(Non)\-LinearRealArith.
 %
This year all divisions with non-linear arithmetic, arrays, and datatypes 
are experimental divisions.
%
The track will run on a
selection of non-incremental \emph{sat} benchmarks from these
logics (as described on page~\pageref{benchmark-selection}).
%
We exclude from the selection all benchmarks containing arrays or datatypes.

>>>>

  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's
    competition introduced the experimental divisions QF\_FPArith
    (excluding the logics QF\_ABVFP, QF\_AUFBVFP, and QF\_ABVFPLRA).
  %
  This year these divisions will be officially counted and no longer be experimental.
  %
  In addition, we add this year new experimental divisions for
  arrays, non-linear arithmetic and for datatypes.  These include the divisions
  QF\_NonLinearIntArith, QF\_NonLinearRealArith,
  QF\_Equality+NonLinearArithm,
  and QF\_Datatypes.
%
  \rationale{Last year's divisions ran successfully, so there
    is no reason to keep them experimental.
    %
    For the new divisions, as before, given the inconsistencies across different
    model producing solvers, we proceed in an experimental fashion to push for
    model standardization.}

@@

\header{Wrapper Tool.}
%
A \emph{wrapper tool} is defined as any solver that calls one or more other SMT
solvers (the \emph{wrapped solvers}) from a different
group of authors to solve distinct subtasks. 
Examples of such subtasks are preprocessing steps or solving a subproblem that belongs to a strict sublogic of the input logic.
For example, a solver using one subsolver to solve the ground abstraction of a
quantified problem would be a wrapper tool.
However, a wrapper tool solving a benchmark of logic A is not allowed to call an SMT solver 
to solve a problem for logic A; even if the problem is just a subproblem.
The system description of a wrapper tool \textbf{must}
explicitly acknowledge and state the \textbf{exact} version of any solvers that
it wraps.  It \textbf{must} further make clear technical innovations by which
the wrapper tool expects to improve on the wrapped solvers.

\header{Derived Tool.}
%
A \emph{derived tool} is defined as any solver that is \emph{based on and
extends} another SMT solver (the \emph{base solver}) from a different
group of authors.  
In contrast to a wrapper tool, 
a derived tool solving a benchmark of logic A is allowed to call an SMT solver 
to solve a problem for logic A.
However, it is not allowed to call more than one different SMT solver to solve a problem over the input logic.
Examples of derived tools are tools that change the strategy selection for the base solver,
tools that add new preprocessing steps on top of the base solver,
tools that add new heuristics or incomplete procedures to a base solver.
The system description of a derived tool
\textbf{must} explicitly acknowledge
the solver it is based on and extends.  It \textbf{must} further make clear
technical innovations by which the derived tool expects to improve on the
original solver.  A derived tool \textbf{must} follow the \emph{naming convention}
{[name of base solver]-[my solver name]}.

@@

\header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
QF\_DataTypes, QF\_Equality,
QF\_Equality+Bitvec,
QF\_Equality+(Non)LinearArith,  
QF\_(Non)LinearIntArith, and QF\_(Non)\-LinearRealArith.
 %
This year all divisions with non-linear arithmetic, arrays, and datatypes 
are experimental divisions.
%
The track will run on a
selection of non-incremental \emph{sat} benchmarks from these
logics (as described on page~\pageref{benchmark-selection}).
